---
title: "A really not so simple document"
author: "Alexa Burko"
output: 
  html_document:
    toc: true
    toc_float: true
---

I'm an R Markdown document! 

toc: true creates a table of contents

# Section 0: Libraries
```{r echo=F, message=F}
library(tidyverse)
```
Echo=F means that that, when knitted, the document will not include the code itself, but
will include the output

Message = F means any warnings or messages will not show in the document

eval = F means that that chunk of code will not run

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

1 tick and then r will also be interpreted as code

**word** makes the words bolded
_word_ makes the words italicized

# Section 3: a tibble
```{r}
plot_df = 
  tibble(
    x = rnorm(1000, sd = 0.5),
  y = 1 + 2 * x + rnorm(1000)
)

head(plot_df)
```

# Section 4: plots

These are plots from our random sample
```{r echo=F, message=F}
ggplot(plot_df, aes(x=x)) + geom_histogram()

ggplot(plot_df, aes(x=x, y=y)) + geom_point()
```
# Section 5: Learning Assessment 2
Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE

Tibble creates a dataframe

Putting anything right after the r at the beginning of the chunk will be the name of that
chunk

The plot shows the distribution of the absolute value of $X$ 
```{r LA2}

set.seed(0)

df = tibble(
  num_var = rnorm(n=500, mean=1),
  log_var = num_var > 0,
  abs_var = abs(num_var))

ggplot(df, aes(x=abs_var)) + geom_histogram()

```
The median is `r round(median(pull(df, num_var)),2)`

The median is `r round(median(df$num_var),2)`

The 2 is rounding the answer to 2 decimal places

The above two pieces of code do the same thing

# Section 6: Formatting

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell


# Section 7: Learning Assessment 3
After the previous code chunk, write a bullet list given the mean, median, and standard deviation of the original random sample

The median is `r round(median(pull(df, num_var)),2)`.
The mean is `r round(mean(pull(df, num_var)),2)`.
The standard deviation is `r round(sd(pull(df, num_var)),2)`.

What if i try to add a histogram 
```{r}
ggplot(plot_df, aes(x=x)) + geom_histogram()
```
